Active galactic nuclei (AGN) are now routinely observed to accelerate outflows of gas, which are commonly thought to play an important role in galaxy evolution by heating and expelling material that is needed for star formation. Therefore, over the past twenty-five years, many observational studies have aimed to verify this situation by comparing observed outflow properties to the requirements and predictions of models of galaxy evolution. However, the true natures of outflows remain unclear due to major uncertainties in deriving key properties from observations. In this thesis, I present a series of detailed studies of nearby active galaxies that develop, verify, and use precise diagnostics of AGN-driven outflow properties to address these sources of uncertainty and robustly determine the impact of outflows on host galaxies. 

I find that when one of the main sources of uncertainty --- the electron density of outflowing gas --- is accounted for, the kinetic powers of the most-commonly-observed outflow phase (warm-ionised gas) are significantly below the requirements of galaxy evolution models. However, multi-wavelength observations reveal that this phase constitutes a small fraction of the total outflowing mass, with the cooler neutral atomic and cold molecular phases dominating in terms of mass and kinetic power. Moreover, I present evidence for AGN-driven outflows being limited to the central regions of galaxies, indicating that outflows do not have a galaxy-wide impact. Finally, despite outflow ionisation/excitation conditions being commonly used to determine acceleration mechanisms, I demonstrate that the link between them is complex; using detailed multi-wavelength diagnostic techniques, I argue that, in the objects studied, AGN jets are the dominant outflow acceleration mechanism. Overall, this work demonstrates the careful considerations that must be made when quantifying the properties of AGN-driven outflows and determining their true role in galaxy evolution, and presents precise techniques that are crucial for this purpose.