\thispagestyle{empty}
Undertaking a PhD in astrophysics (and over ten years in higher education in general) is an immense feat, and while I'm incredibly proud of the work and determination that it has taken to reach this point, I would not have been able to do it without a lot of help and support, for which I am incredibly thankful.

First and foremost, I thank my supervisor, Clive Tadhunter, for his invaluable assistance and mentorship, both during my PhD and before. I could not have asked for a better supervisor, and I have an immense amount of respect for you as a scientist (in particular your healthy scepticism, which is contagious). Beyond academia, it has been a pleasure to get to know you over the past seven years --- I have greatly enjoyed our conversations about science and almost everything else, and I look forward to keeping in touch. It was an absolute honour to work with you.

There are many others within academia and education who have helped me immensely, yet are too many to name here. Particular thanks to Dr. Nolan, my Sixth Form physics teacher, without whom I likely would have never made it into an astrophysics course, and Vik Dhillon, without whom I would not have had the opportunity to work on La Palma, which turned out to be the most important and influential year of my life thus far. My thanks to all of those who I had the pleasure of knowing and working with on La Palma (including the ING + ORM staff, and the ING and NOT student cohort of 2018--2019), as well as all of those in the Sheffield astrophysics group during my time here. Special thanks to Paul Kerry for his patience and support on the computing side of things --- the Sheffield astrogroup couldn't do our job without you.

Along with astronomy, my other main passion is music, which I've attempted to include in this thesis by having the quotes at the start of each chapter be from songs that have had a particular meaning to me throughout my PhD --- many thanks to the artists behind those songs. Thank you also to the Sheffield / South Yorkshire underground metal scene for being an ace community during my time in the city, and a special thank you to my Void Maw bandmates Bill and Shaun for not only allowing me to achieve a life goal of writing and playing my own music live (as well as putting an AGN jet in the band logo), but also for their understanding and patience with me finishing this PhD.

\newpage
\thispagestyle{empty}
Thanks also to my friends who have supported me during this period --- unfortunately, I don't have the space here to do justice to my appreciation of all of you. Kahleel: eternal thanks for your endless support and friendship; it has been a pleasure to grow and evolve with you. David: thank you for your years of support and understanding --- I would say I'm the first astrophysicist to cite a neuroscientist, but given how much survey astronomers love statistics, I'd say it's unlikely. Kuba \& Olivia: thanks for your support and all of the good times, and apologies for formally tying you to astrophysics with this acknowledgement. Thanks also to Rob for being a great friend (as well as housemate for the majority of my PhD), and for all of our brilliant conversations. Importantly, I give my thanks and love to Dario Napodano and Alan Chopping, who played crucial roles in my life, but are no longer here for me to thank in person. \\

And of course, my endless thanks and much love to my family --- Mum, Dad, and Dan --- for supporting me through the past ten years. I absolutely could not have done this without you, and I cannot express how much I appreciate it. \\

Finalmente, quiero agradecer y dar mucho amor a mi guapi Nebaí. Me has ayudado mas que podrias saber, y te quiero mucho mas que podria decir. Muchisimas gracias por todo, y tengo muchas ganas de empezar la proxima etapa de nuestra vida. Te amito.
